Gamification can Change the Traditonal Educational System

### 2024-04-19 paper/paper.qmd
added the last references

Like I mentioned before gamification has to potential to change the traditional educational system, but in order to do that need to design it in a way that truly benefits the students. A leading expert in gamification and behavioral drive, Yu-kai Chou, has a create framework for gamification called the Octalysis Framework(@fig-framework).Looking at the framework there are eight core drives: Epic Meaning, Accomplishment, Empowerment, Ownership, Social Influence, Scarcity, Unpredictability, and Avoidance. For even more in depth explanation, please visit Yu-kai website:https://yukaichou.com/gamification-examples/octalysis-complete-gamification-framework/.

Let us see how this framework applies to our study, for this example we will using social gamification group, since it one of the better performing groups with game elements. Epic Meaning category it is might but some students as they believe if they do well in this course, it could lead to some future goal like their dream job. Accomplishment is achieved by the meaningful challenges provided in each module and achievements. Empowerment is achieved by peer reviews and feedback from the teacher as well. Ownership is achieved as they can customize their profiles and status. Social Influence is achieved by being able to add friends and being able to features similar to Twitter(known as X now). This study has 5 out of 8 core drives mention from the framework.

Another example that we want to apply this framework is on a popular gamification language learning app, called Duolingo. Duolingo is a free app that has millions of user ranging from public students in third world countries to even Hollywood stars. Yu-kai Chou website provides an analysis for Duolingo, which has 6 out of 8 elements of the framework and here I am going to highlight some of the elements. Firstly, Epic Meaning is to learn a language and the app even asks the user when creating an account what is their purpose for learning new language. Secondly, Ownership, users have a currency call Lingots which allows players to buy Power-Ups(ways to make the player stronger) such as streak freeze and to buy clothes for their player character. Lastly, it has Scarcity and Avoidance as player have a limited amount of lives and if they lose then they can no longer play for a certain of time.

@@

Another weakness of this study is that study it reproduce is about 10 years old. This mean that data may not hold up as well. But there are not many gamification studies that compare treatment to a experiment group, and with open source data to boot. Also, Duolingo is popular language learn app, which use gamification and it has millions of active users which suggest that gamification is not a dead field and it is clearly effective for learning languages.

@@

Like I mentioned before, this paper shows that gamification has potential to surpass traditional educational system. In future studies, more attention should be put into designing the gamification aspect. The Octalysis framework should be used and the design should it is best to meet all 8 core drives. Furthermore, Yu-kai is open to collaboration and consulting so that could make the design even better as there is more than just this framework that he talks about on his website. In addition, there should focus on social elements as well since that experiement did well in post tests. Lastly, this design is probably going to need multiple iterations and constant feedback from the students to further improve it and to allow it eventually surpass the traditional education system.
\newpage

>>>>

Like I mentioned before gamification has to potential to change the traditional educational system, but in order to do that need to design it in a way that truly benefits the students. A leading expert in gamification and behavioral drive, Yu-kai Chou, has a create framework for gamification called the Octalysis Framework(@fig-framework).Looking at the framework there are eight core drives: Epic Meaning, Accomplishment, Empowerment, Ownership, Social Influence, Scarcity, Unpredictability, and Avoidance. For even more in depth explanation, please visit Yu-kai website(@yukai).

Let us see how this framework(@fig-framework) applies to our study, for this example we will using social gamification group, since it one of the better performing groups with game elements. Epic Meaning category it is might but some students as they believe if they do well in this course, it could lead to some future goal like their dream job. Accomplishment is achieved by the meaningful challenges provided in each module and achievements. Empowerment is achieved by peer reviews and feedback from the teacher as well. Ownership is achieved as they can customize their profiles and status. Social Influence is achieved by being able to add friends and being able to features similar to Twitter(known as X now). This study has 5 out of 8 core drives mention from the framework.

Another example that we want to apply this framework(@fig-framework) is on a popular gamification language learning app, called Duolingo(@Duolingo). Duolingo is a free app that has millions of user ranging from public students in third world countries to even Hollywood stars. Yu-kai Chou website(@yukai) provides an analysis for Duolingo, which has 6 out of 8 elements of the framework and here I am going to highlight some of the elements. Firstly, Epic Meaning is to learn a language and the app even asks the user when creating an account what is their purpose for learning new language. Secondly, Ownership, users have a currency call Lingots which allows players to buy Power-Ups(ways to make the player stronger) such as streak freeze and to buy clothes for their player character. Lastly, it has Scarcity and Avoidance as player have a limited amount of lives and if they lose then they can no longer play for a certain of time.

@@

Another weakness of this study is that study it reproduce is about 10 years old. This mean that data may not hold up as well. But there are not many gamification studies that compare treatment to a experiment group, and with open source data to boot. Also, Duolingo(@Duolingo) is popular language learn app, which use gamification and it has millions of active users which suggest that gamification is not a dead field and it is clearly effective for learning languages.

@@

Like I mentioned before, this paper shows that gamification has potential to surpass traditional educational system. In future studies, more attention should be put into designing the gamification aspect. The Octalysis framework should be used and the design should it is best to meet all 8 core drives. Furthermore, Yu-kai is open to collaboration and consulting so that could make the design even better as there is more than just this framework that he talks about on his website(@yukai). In addition, there should focus on social elements as well since that experiment did well in post tests. Lastly, this design is probably going to need multiple iterations and constant feedback from the students to further improve it and to allow it eventually surpass the traditional education system.
\newpage
